\documentclass[12pt,a4paper]{article}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{float}

% ── Colors ──
\definecolor{meridian}{HTML}{6366F1}
\definecolor{codebg}{HTML}{1E1B4B}
\definecolor{lightgray}{HTML}{F3F4F6}
\definecolor{darktext}{HTML}{1A1A2E}

% ── Hyperlinks ──
\hypersetup{
  colorlinks=true,
  linkcolor=meridian,
  urlcolor=meridian,
  citecolor=meridian,
}

% ── Header/Footer ──
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{meridian}{\textbf{Meridian Integration Platform}}}
\fancyhead[R]{\textcolor{gray}{Technical Report}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ── Code Listings ──
\lstdefinestyle{code}{
  backgroundcolor=\color{lightgray},
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  rulecolor=\color{meridian!30},
  tabsize=2,
  showstringspaces=false,
}

% ── Title Formatting ──
\titleformat{\section}{\Large\bfseries\color{meridian}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{darktext}}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{darktext}}{\thesubsubsection}{1em}{}

% ── Document ──
\begin{document}

% ══════════════════════════════════════════════════════════
%  TITLE PAGE
% ══════════════════════════════════════════════════════════
\begin{titlepage}
\centering
\vspace*{3cm}

{\Huge\bfseries\textcolor{meridian}{Meridian Integration Platform}}\\[0.8cm]
{\Large\textcolor{gray}{Enterprise SAP S/4HANA $\leftrightarrow$ FinSight Analytics}}\\[2cm]

{\large\bfseries Technical Project Report}\\[0.5cm]
{\large Version 1.0}\\[2cm]

\begin{tabular}{rl}
\textbf{Project:} & Meridian Integration Platform \\
\textbf{Author:}  & Vardhan \\
\textbf{Date:}    & July 19, 2026 \\
\textbf{Stack:}   & Next.js 16, TypeScript, Tailwind CSS, Recharts \\
\textbf{Deployment:} & Vercel (Production) \\
\textbf{Repository:} & \texttt{vardhan23v/meridian-integration-platform} \\
\end{tabular}

\vfill
{\small\textcolor{gray}{Confidential --- Meridian Manufacturing Ltd.}}
\end{titlepage}

% ══════════════════════════════════════════════════════════
%  TABLE OF CONTENTS
% ══════════════════════════════════════════════════════════
\tableofcontents
\newpage

% ══════════════════════════════════════════════════════════
%  1. EXECUTIVE SUMMARY
% ══════════════════════════════════════════════════════════
\section{Executive Summary}

The \textbf{Meridian Integration Platform} is an enterprise-grade web application that provides a unified monitoring and management dashboard for SAP S/4HANA $\leftrightarrow$ FinSight Financial Analytics integrations. Built with a modern monorepo architecture, the platform delivers:

\begin{itemize}[leftmargin=2em]
  \item Real-time pipeline throughput and service latency monitoring
  \item Integration job orchestration with one-click triggering
  \item Dead Letter Queue (DLQ) management with retry and resolution workflows
  \item Role-based authentication and session management
  \item A premium glassmorphic UI with liquid-glass design tokens
\end{itemize}

The platform is deployed on \textbf{Vercel} and accessible at:\\
\url{https://web-beta-six-n0a0d29mql.vercel.app}

% ══════════════════════════════════════════════════════════
%  2. ARCHITECTURE OVERVIEW
% ══════════════════════════════════════════════════════════
\section{Architecture Overview}

\subsection{Monorepo Structure}

The project follows a \textbf{pnpm workspace monorepo} pattern:

\begin{lstlisting}[style=code]
meridian-integration-platform/
  apps/
    web/          # Next.js 16 frontend (Turbopack)
    api/          # NestJS backend API
  packages/
    shared/       # Shared TypeScript interfaces & utilities
  package.json    # Root workspace config
  pnpm-workspace.yaml
\end{lstlisting}

\subsection{Technology Stack}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Layer} & \textbf{Technology} \\
\midrule
Frontend Framework & Next.js 16.2.10 (App Router, Turbopack) \\
Language           & TypeScript 5.x (strict mode) \\
Styling            & Tailwind CSS 4.x + custom Liquid-Glass design tokens \\
Charts             & Recharts (AreaChart, BarChart, LineChart sparklines) \\
State Management   & Zustand (persisted auth store) \\
Data Fetching      & TanStack React Query v5 \\
HTTP Client        & Axios with JWT interceptors \\
Form Handling      & React Hook Form + Zod validation \\
Package Manager    & pnpm 11.13.0 (workspaces) \\
Deployment         & Vercel (edge-optimized, serverless functions) \\
\bottomrule
\end{tabularx}
\caption{Technology stack overview}
\end{table}

\subsection{Data Flow}

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Client} renders pages via Next.js App Router (SSR/SSG where possible).
  \item \textbf{React Query hooks} call the \texttt{apiClient} (Axios instance).
  \item \texttt{apiClient} injects JWT Bearer token via request interceptor.
  \item \textbf{Next.js API Routes} (\texttt{/api/v1/*}) serve mock data (serverless functions on Vercel).
  \item Responses conform to the \texttt{ApiResponse<T>} envelope: \texttt{\{data: T\}}.
  \item React Query caches responses with configurable \texttt{staleTime} and \texttt{refetchInterval}.
\end{enumerate}

% ══════════════════════════════════════════════════════════
%  3. SHARED TYPE SYSTEM
% ══════════════════════════════════════════════════════════
\section{Shared Type System (\texttt{@meridian/shared})}

The \texttt{packages/shared} package exports all domain interfaces consumed by both the frontend and backend.

\subsection{Dashboard Types}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Interface} & \textbf{Purpose} \\
\midrule
\texttt{DashboardOverview} & Top-level aggregate: stats, pipelines, services, events \\
\texttt{PipelineStatus}    & Pipeline ID, name, status (healthy/warning/error), throughput \\
\texttt{ServiceHealth}     & Service name, status (up/down/degraded), latency, uptime \\
\texttt{IntegrationEvent}  & Event ID, type, status (success/failed/pending), message \\
\texttt{DashboardMetrics}  & Time-series arrays: pipelineThroughput, serviceLatency, eventVolume \\
\texttt{MetricPoint}       & Single data point: \texttt{\{timestamp: string, value: number\}} \\
\bottomrule
\end{tabularx}
\caption{Dashboard type interfaces}
\end{table}

\subsection{Integration Job Types}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Interface} & \textbf{Purpose} \\
\midrule
\texttt{IntegrationJob}     & Job ID, name, status, source, destination, scheduling \\
\texttt{TriggerJobResponse} & Job trigger acknowledgement \\
\bottomrule
\end{tabularx}
\caption{Integration job type interfaces}
\end{table}

\subsection{Dead Letter Queue Types}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Interface} & \textbf{Purpose} \\
\midrule
\texttt{DLQMessage}        & Message ID, topic, partition, offset, payload, error, retry count \\
\texttt{DLQActionResponse} & Retry/resolve action acknowledgement \\
\bottomrule
\end{tabularx}
\caption{DLQ type interfaces}
\end{table}

% ══════════════════════════════════════════════════════════
%  4. FRONTEND PAGES & COMPONENTS
% ══════════════════════════════════════════════════════════
\section{Frontend Pages \& Components}

\subsection{Routing Architecture}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Route} & \textbf{Group} & \textbf{Description} \\
\midrule
\texttt{/}                         & ---        & Redirects to \texttt{/login} \\
\texttt{/login}                    & (auth)     & JWT authentication form \\
\texttt{/dashboard}                & (dashboard)& Main overview with stat cards, charts, events \\
\texttt{/dashboard/jobs}           & (dashboard)& Integration jobs table with trigger actions \\
\texttt{/dashboard/dlq}            & (dashboard)& Dead letter queue with retry/resolve actions \\
\texttt{/dashboard/reconciliation} & (dashboard)& Reconciliation engine (placeholder) \\
\bottomrule
\end{tabularx}
\caption{Application routes}
\end{table}

\subsection{Component Hierarchy}

\subsubsection{Dashboard Page (\texttt{/dashboard})}

\begin{itemize}[leftmargin=2em]
  \item \textbf{StatCard} (×4): Total Pipelines, Active Pipelines, Total Events, Failed Events. Each card has accent-colored icon, animated counter, and hover glow effect.
  \item \textbf{PipelineStatusList} → \textbf{PipelineCard} (×3): Displays per-pipeline status badge, Recharts sparkline of throughput, and last-run timestamp.
  \item \textbf{ServiceHealthGrid} (×3): Service cards with animated status dot, latency progress bar, and uptime indicator.
  \item \textbf{MetricsChart} (×2): Pipeline Throughput (area chart) and Service Latency (bar chart) powered by Recharts with gradient fills.
  \item \textbf{EventsFeed}: Scrollable event list with relative timestamps and animated slide-in for new entries.
\end{itemize}

\subsubsection{Integration Jobs Page (\texttt{/dashboard/jobs})}

\begin{itemize}[leftmargin=2em]
  \item \textbf{IntegrationJobsTable}: Full-width data table with columns for Job Name, Status, Source→Destination, Last Run, Next Run, and a Trigger action button.
  \item Uses \texttt{useMutation} for one-click job triggering with optimistic UI updates.
\end{itemize}

\subsubsection{Dead Letter Queue Page (\texttt{/dashboard/dlq})}

\begin{itemize}[leftmargin=2em]
  \item \textbf{DLQTable}: Data table with Message ID, Topic, Status, Error, Payload preview, Timestamp, and Retry/Resolve action buttons.
  \item Truncated payload previews with full-text tooltips.
\end{itemize}

% ══════════════════════════════════════════════════════════
%  5. API ROUTES
% ══════════════════════════════════════════════════════════
\section{API Routes (Mock Backend)}

All API routes are implemented as \textbf{Next.js Route Handlers} under \texttt{src/app/api/v1/}:

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Method} & \textbf{Endpoint} & \textbf{Description} \\
\midrule
POST & \texttt{/api/v1/auth/login}          & Validates credentials, returns JWT + user object \\
GET  & \texttt{/api/v1/dashboard/overview}   & Returns stats, pipelines, services, events \\
GET  & \texttt{/api/v1/dashboard/metrics}    & Returns time-series throughput, latency, volume \\
GET  & \texttt{/api/v1/dashboard/events}     & Returns recent integration events \\
GET  & \texttt{/api/v1/integrations}         & Returns integration job list \\
POST & \texttt{/api/v1/integrations/trigger}  & Triggers a named job \\
GET  & \texttt{/api/v1/dlq}                  & Returns DLQ message list \\
POST & \texttt{/api/v1/dlq/[id]/retry}       & Retries a dead-letter message \\
POST & \texttt{/api/v1/dlq/[id]/resolve}     & Resolves a dead-letter message \\
\bottomrule
\end{tabularx}
\caption{API endpoint reference}
\end{table}

% ══════════════════════════════════════════════════════════
%  6. UI/UX DESIGN SYSTEM
% ══════════════════════════════════════════════════════════
\section{UI/UX Design System}

\subsection{Liquid-Glass Token System}

The platform implements a comprehensive \textbf{Liquid-Glass} design system defined entirely in CSS custom properties:

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Token Category} & \textbf{Tokens} \\
\midrule
Glass Opacity    & \texttt{--glass-opacity-light/medium/strong/subtle} \\
Glass Blur       & \texttt{--glass-blur-sm/md/lg/xl} (8px--40px) \\
Border Luminance & \texttt{--glass-border-luminance(-strong/-subtle)} \\
Glow Colors      & \texttt{--glow-accent/success/warning/danger/white} \\
Surface BGs      & \texttt{--glass-bg/glass-bg-strong/glass-bg-subtle} \\
Shadows          & \texttt{--glass-shadow/strong/elevated} \\
\bottomrule
\end{tabularx}
\caption{CSS custom property tokens}
\end{table}

\subsection{Utility Classes}

\begin{itemize}[leftmargin=2em]
  \item \texttt{.glass} --- Standard glassmorphic panel with backdrop blur
  \item \texttt{.glass-strong} --- Higher opacity, stronger blur
  \item \texttt{.glass-subtle} --- Minimal glass effect
  \item \texttt{.glass-surface} / \texttt{.glass-elevated} --- Legacy surface variants
  \item \texttt{.glow} / \texttt{.glow-strong} --- Focus/hover glow rings
  \item \texttt{.animate-fade-in-up} / \texttt{.animate-blob} / \texttt{.animate-float} --- Motion
\end{itemize}

\subsection{Dark Mode}

Full dark mode support via \texttt{@media (prefers-color-scheme: dark)} with recalculated token values for:
\begin{itemize}[leftmargin=2em]
  \item Inverted surface backgrounds (deep navy \texttt{\#0a0a14})
  \item Adjusted glass opacity for dark surfaces
  \item Strengthened glow intensities for dark contexts
  \item Screen blend mode on animated background orbs
\end{itemize}

% ══════════════════════════════════════════════════════════
%  7. AUTHENTICATION
% ══════════════════════════════════════════════════════════
\section{Authentication}

\subsection{Login Flow}

\begin{enumerate}[leftmargin=2em]
  \item User visits \texttt{/} → redirected to \texttt{/login}.
  \item Login form validates with \textbf{Zod} schema (email format, password $\geq$ 6 chars).
  \item \texttt{POST /api/v1/auth/login} validates credentials server-side.
  \item On success: JWT \texttt{accessToken} stored in \texttt{localStorage}; user object persisted in Zustand store.
  \item Axios interceptor attaches \texttt{Bearer <token>} to all subsequent API requests.
  \item On 401 response: interceptor clears token and redirects to \texttt{/login}.
\end{enumerate}

\subsection{Test Credentials}

\begin{tcolorbox}[colback=meridian!5, colframe=meridian, title=Demo Login]
\textbf{Email:} \texttt{admin@meridian.com}\\
\textbf{Password:} \texttt{Meridian@2026}
\end{tcolorbox}

% ══════════════════════════════════════════════════════════
%  8. DEPLOYMENT
% ══════════════════════════════════════════════════════════
\section{Deployment}

\subsection{Vercel Configuration}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Framework:} Automatically detected as Next.js
  \item \textbf{Build Command:} \texttt{pnpm --filter @meridian/shared build \&\& pnpm --filter @meridian/web build}
  \item \textbf{Output:} \texttt{/vercel/output} (static pages + serverless functions)
  \item \textbf{Region:} Washington, D.C. (iad1)
  \item \textbf{Node.js:} 25.9.0
\end{itemize}

\subsection{Production URLs}

\begin{itemize}[leftmargin=2em]
  \item \textbf{Primary:} \url{https://web-beta-six-n0a0d29mql.vercel.app}
  \item \textbf{Deployment:} \url{https://web-mxkg1fnq5-vardhan23vs-projects.vercel.app}
\end{itemize}

\subsection{Build Output}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Route} & \textbf{Type} & \textbf{Notes} \\
\midrule
\texttt{/}              & Static (○) & Redirect to \texttt{/login} \\
\texttt{/login}         & Static (○) & Prerendered \\
\texttt{/dashboard}     & Static (○) & Client-side data fetching \\
\texttt{/dashboard/dlq} & Static (○) & Client-side data fetching \\
\texttt{/dashboard/jobs} & Static (○) & Client-side data fetching \\
\texttt{/api/v1/*}      & Dynamic (ƒ) & Serverless functions \\
\bottomrule
\end{tabularx}
\caption{Build output routes}
\end{table}

% ══════════════════════════════════════════════════════════
%  9. KNOWN ISSUES & FUTURE WORK
% ══════════════════════════════════════════════════════════
\section{Known Issues \& Future Work}

\subsection{Current Limitations}

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Mock data only}: All API routes return static mock data; no real SAP/FinSight integration yet.
  \item \textbf{Reconciliation page}: Currently a placeholder; variance reports not yet implemented.
  \item \textbf{Executive Overview}: Links to \texttt{/dashboard} (same page); needs dedicated analytics view.
  \item \textbf{JWT stored in localStorage}: Production should use HttpOnly cookies.
  \item \textbf{No middleware auth guard}: Client-side routing handles protection; Edge middleware is a pass-through.
\end{enumerate}

\subsection{Planned Enhancements}

\begin{itemize}[leftmargin=2em]
  \item Connect real NestJS backend (\texttt{apps/api}) with PostgreSQL database
  \item Implement WebSocket-based real-time event streaming
  \item Add reconciliation variance reports with drill-down analysis
  \item Role-based access control (RBAC) using the \texttt{UserRole} enum
  \item End-to-end tests with Playwright
  \item CI/CD pipeline with GitHub Actions
\end{itemize}

% ══════════════════════════════════════════════════════════
%  10. CONCLUSION
% ══════════════════════════════════════════════════════════
\section{Conclusion}

The Meridian Integration Platform demonstrates a production-ready enterprise dashboard with a modern React stack, comprehensive type safety through shared interfaces, and a premium glassmorphic UI design system. The monorepo architecture enables clean separation between the frontend, backend, and shared code while maintaining a unified deployment pipeline through Vercel.

\vspace{1cm}
\noindent\rule{\textwidth}{0.4pt}
\begin{center}
\textcolor{gray}{\small Generated on July 19, 2026 --- Meridian Integration Platform v1.0}
\end{center}

\end{document}
